---
title: "Employees Turnover"
output: html_notebook
---



The goal of this notebook is to predict an Employee's risk of quitting (with a Survival Analysis Model). First, I clean and explore the dataset to prepare it for analyses. After reviewing the statistical organization's and performance characteristics through EDA and feature engineering techniques, I generate models that predict employee turnover. The first regression model takes a large set of predictors while the second model includes only ...

This notebook predict the Turnover Employee's, using the workflow bellow:

    1) Data Import and Clean Data (Turnover.csv)
    2) EDA
    3) Feature Engineering
    4) Significance Testing
    5) Logistic Regression Modeling and Validation
    

For this notebook, we are using the Turnover.csv file that contains, the following columns:

      •	stag - Experience (time)
      •	event - Employee turnover
      •	gender - Employee's gender, female(f), or male(m)
      •	age - Employee's age (year)
      •	industry - Employee's Industry
      •	profession - Employee's profession
      • traffic - From what pipelene employee came to the company. 
      •	coach - Presence of a coach (training) on probation
      •	head_gender - head (supervisor) gender
      •	greywage - The salary does not seem to the tax authorities. Greywage in Russia or Ukraine means that the employer (company) pay
      •	way - Employee's way of transportation
      •	extraversion - Extraversion score
      •	independ - Independend score
      •	selfcontrol - Selfcontrol score
      •	anxiety - Anxiety score
      •	novator - Novator score


#Libraries/Dependencies:
```{r}
install.packages("nlme")
```

```{r}
suppressMessages(library(mgcv))
suppressMessages(library(tidyverse))
suppressMessages(library(lubridate))
suppressMessages(library(broom))
suppressMessages(library(survival))
suppressMessages(library(survminer))
suppressMessages(library(lubridate))
suppressMessages(library(dplyr)) # Data Manipulation
suppressMessages(library(ggplot2)) # Visualization
suppressMessages(library(corrplot))
suppressMessages(library(RColorBrewer))
suppressMessages(library(caTools)) # Prediction: Splitting Data
library(car) # Prediction: Checking Multicollinearity
library(ROCR) # Prediction: ROC Curve
library(e1071) # Prediction: SVM, Naive Bayes, Parameter Tuning
library(rpart) # Prediction: Decision Tree
library(rpart.plot) # Prediction: Decision Tree
```




#Read data
```{r}
data <- read.csv('turnover.csv', header = TRUE, sep = ',')
head(data, 10)
```
###EXPLORATORY Data Analysis:
```{r}
str(data)
```
#Data dimension+Columns names+Summary:
```{r}
dim(data)
colnames(data)     #dimension of 1129 rows and 16 columns 
summary(data)
```


#Variables check---------------------------------------
#Continuous variables (event= (Turnover or active),stag(time to turnover),Age, Independence, extraversion, selfcontrol, Anxiety, Novator)
```{r}
#Distribution Plot:
par(mfrow=c(1,3))
hist(data$event, col="green")
hist(data$stag, col="red")
hist(data$age, col="blue")
hist(data$anxiety, col="yellow")
hist(data$extraversion, col="green")
hist(data$selfcontrol, col="pink")
hist(data$independ, col="blue")
hist(data$novator, col="red")
```

#Discret variables (Gender, Manager gender, Coach, greywage, traffic, Profession, Transport,Industry)
```{r}
#Gender
barplot(table(data$gender), ylab="Count",xlab="gender distribution", col=c(2,8), names.arg=c("f", "m"))

# Manager Gender
barplot(table(data$head_gender), ylab="Count",xlab="Manager gender distribution", col=c(1,6), names.arg=c("f", "m"))


# Coach
barplot(table(data$coach), ylab="Count",xlab="Coach distribution", col=c(0,8,5), names.arg=c("No coach", "My head", "Yes"))

#Greywage:
barplot(table(data$greywage), ylab="Count",xlab="Greywage", col=c(2,7), names.arg=c("Grey", "White"))

#Traffic:
data |>
  group_by(traffic) |>
  summarize(turnover_rate = mean(event), .groups = 'drop') |>
  ggplot(aes(traffic, turnover_rate))  + 
  geom_bar(stat = "identity", aes(fill = traffic)) + 
  theme(axis.title.x = element_blank()) + ylab("Turnover Rate") + 
  theme(legend.position = "none") + scale_fill_brewer(palette = "Paired") + 
  ggtitle("Turnover Rate by traffic") + 
  theme(text = element_text(size = 15))

#Profession

data$profession<-str_replace_all(data$profession,"<f1>", "c") #Replace error data:

Table_profession<-table(data$profession,data$event)
data_table_profession<-as.data.frame(Table_profession)
Table_profession<-subset(data_table_profession,Var2==1)
print(Table_profession)


Table_profession$Var1 <- factor(Table_profession$Var1, levels =Table_profession$Var1[order(-Table_profession$Freq)])

Plot_profession<-ggplot(Table_profession, aes(x=Var1,y=Freq,fill=Var1)) +
 geom_bar(stat='identity') +theme(axis.text.x = element_text(angle = 90, hjust = 1))

print(Plot_profession)



#Industry VS Turnover 

Table_industry<-table(data$industry,data$event)
data_table_industry<-as.data.frame(Table_industry)
Table_industry<-subset(data_table_industry,Var2==1)
print(Table_industry)


Table_industry$Var1 <- factor(Table_industry$Var1, levels =Table_industry$Var1[order(-Table_industry$Freq)])
plot_industry<-ggplot(Table_industry, aes(x=Var1,y=Freq,fill=Var1)) +
 geom_bar(stat='identity') +theme(axis.text.x = element_text(angle = 90, hjust = 1))

print(plot_industry)



# Transport (way)
data |>
  group_by(way) |>
  summarize(turnover_rate = mean(event), .groups = 'drop') |>
  ggplot(aes(way, turnover_rate))  + 
  geom_bar(stat = "identity", aes(fill = way)) + 
  theme(axis.title.x = element_blank()) + ylab("Turnover Rate") + 
  theme(legend.position = "none") + scale_fill_brewer(palette = "Paired") + 
  ggtitle("Turnover Rate by way") + 
  theme(text = element_text(size = 15))
```
see link for salary greywage : https://blogs.elenasmodels.com/ukraine-white-black-grey-wages/
Grey wage = Employees are paid cash partially, in addition to the official wage (“grey” wages”).
White Wage: employees receive “white” (fully official) wages.

#Explanatory of Employee's Turnover VS active employee's:
```{r}
#Remove columns not needed:
Data_filter <- data |>
  select(-c("greywage","head_gender","profession","industry","traffic","coach","way","extraversion","independ","selfcontrol","anxiety","novator"))

#Convert data columns that can be converted
Cols <-c("event","stag","gender","age")
Data_filter[Cols] <- lapply(Data_filter[Cols], factor)

#Total employees Turnover VS Active:
options(repr.plot.width = 4, repr.plot.height = 4)
Data_filter %>%
  group_by(event) %>%
  ggplot(aes(factor(event))) + geom_bar(aes(fill = event)) + 
  scale_x_discrete(labels = c("active","Turnover" )) + 
  theme(axis.title.x = element_blank()) + ylab("Employee Turnover") + 
  theme(legend.position = "none") + 
  geom_text(stat = "count", aes(label = ..count..), vjust = -.5) + 
  theme(text = element_text(size = 10)) + 
  ggtitle("Total turnover VS active Employees ") + 
  scale_fill_brewer(palette = "Paired")
```
The graph above shows status employee's (Turnover or No).

The  graph indicates that there are 558 active employees and 571 inactive employees (Turnover done) in the dataset (n = 1129). The data on inactive employees will be used in the machine learning portions of this notebook as predictions of turnover employee's.

#Correlation Table (Numeric features)
```{r}
Correlation<-data[,c("stag","event","age","anxiety","extraversion","novator","selfcontrol","independ")]

cor(Correlation)
```
#We do not see a good correlation between those features.


#Distribution on time: 
```{r}
data %>%
    mutate(Turnover_type = factor(ifelse(event == 1, "Turnover", "Active"))) %>%
    select(Turnover_type, stag) %>%
    ggplot(aes(x = stag, colour = Turnover_type)) + 
    geom_density() + 
    ggtitle("Turnover vs Active")
```
Looking at the graph above we can tell that experience (stag) has a very weak correlation with employee quitting so we can tell that experience (time) is not a major factor on employee resigning




Kaplan-Meier test is used in our case to calculate the  probability to stay in a compagny with different parameters.
#GENERAL Kaplan Maier without covariates:

```{r}

fit_KM <- survfit(Surv(stag,event) ~ 1, data = data)
summary(fit_KM)
fit_KM
plot(fit_KM, mark.time = TRUE,
     main = "Kaplan-Meier estimator",
     ylab = "Turnover  probability",
     xlab = "time (Months)")

```
Let's focus on each parameter (Covariates):
1- AGE: we decide to create 4 groups less than 30 for Young, less than 40 for middle age, Less than 50 for Old Age and more than 50
```{r}
#Age parameter/KM:
data$AgeGroup <- ifelse(data$age<30 , "Young employee",
                        ifelse(data$age<40, "Middle Age",
                              ifelse(data$age<50, "Old ages", "others")
                              )
                        )

fit_KM_GroupAGE<- survfit(Surv(stag, event) ~ AgeGroup, data = data)
summary(fit_KM_GroupAGE)
plot(fit_KM_GroupAGE,col = 1:4, mark.time = TRUE,
     main = "Kaplan-Meier estimator for age group",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomleft", col = 1:4, lty = 1, legend = c("Middle aged [30Yo,40Yo[", "Old [40Yo,50Yo[", "Young Adult <30Yo" ,"elderly >=50Yo"))
survdiff(Surv(stag, event) ~ AgeGroup, data = data)

```
We can conclude that there is a significant difference between one of  the 4 groups --> Pvalue=0.02 <5%
But we can see that there is an interesting difference in the middle age -> Let's reduce groups to two groups (Less than 35 and more than 35Y)
We can also see that the more than 50 years old (have no enough data)

```{r}
#2 groups ages:

data$Age_Group <- ifelse(data$age<=35 , "Less 35Y", "More 35Y")
                        
fit_KM_Group_AGE<- survfit(Surv(stag, event) ~ Age_Group, data = data)
summary(fit_KM_Group_AGE)
plot(fit_KM_Group_AGE,col = 1:4, mark.time = TRUE,
     main = "Kaplan-Meier estimator for age group",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomleft", col = 1:4, lty = 1, legend = c("Less than 35", "More than 35"))
survdiff(Surv(stag, event) ~ Age_Group, data = data)
```
#the pvalue = 1e-07 < 5%, there is a significant difference between the 2 ages groups (Less and more than 35Y)
we going to keep those 2 categories ages to study the rest of data.

```{r}
#Gender Parameter KM:
fit_KM_Gender<-  survfit(Surv(stag, event) ~ gender, data = data)
summary(fit_KM_Gender)
plot(fit_KM_Gender,col = 1:2, mark.time = TRUE,
     main = "Kaplan-Meier estimator for gender group",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomright", col = 1:2, lty = 1, legend = c("WOMEN", "MEN"))
survdiff(Surv(stag, event) ~ gender, data = data)


```
p value = 0.1 >5% the difference between gender group is not significant = The sex of employee does not change the probability of turnover
Let's not consider the Employees sex for the rest of study.

#Manager Gender Parameter KM:
```{r}
fit_KM_ManagerGender<- survfit(Surv(stag, event) ~ head_gender, data = data)
summary(fit_KM_ManagerGender)
plot(fit_KM_ManagerGender,col = 1:2, mark.time = TRUE,
     main = "Kaplan-Meier estimator for gender group",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomright", col = 1:2, lty = 1, legend = c("WOMEN", "MEN"))
survdiff(Surv(stag, event) ~ head_gender, data = data)
```
#No significant parameter (Manager gender) p=0.3 >5%
Let's remove this parameter for the rest of study

#Profession
```{r}
fit.KM.profession<- survfit(Surv(stag, event) ~ profession, data = data)
summary(fit.KM.profession)
plot(fit.KM.profession,col = 1:15, mark.time = TRUE,
     main = "Kaplan-Meier estimator for profession group",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomright", col = 1:4, lty = 1, legend = c("Finance", "Accounting","Bis","Commercial","Consult","Engineer","etc","HR","IT","LAW","Manage","Marketing","PR","Sales","Teaching"))
survdiff(Surv(stag, event) ~ profession, data = data)
```

 p= 0.009 is sifnificant -> But not easy to study 16 professions
 Let's try to analyse professions and find a relations 


According to the general KM profession model + the previous distribution, I tried to select a group of 6 interesting profession 

```{r}
#Profession group 
data$ProfessionGroup <- ifelse(data$profession == "HR" , "HR",
                        ifelse(data$profession == "Sales", "Sales",
                        ifelse(data$profession == "IT", "IT",
                        ifelse(data$profession == "etc", "etc",
                        ifelse(data$profession == "BusinessDevelopment", "BusinessDevelopment", "others")
                              ))))
                        
fit.KM.ProfessionGroup<- survfit(Surv(stag, event) ~ ProfessionGroup, data = data)
summary(fit.KM.ProfessionGroup)
plot(fit.KM.ProfessionGroup,col = 1:6, mark.time = TRUE,
     main = "Kaplan-Meier estimator for Profession groups3",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomleft", col = 1:6, lty = 1, legend = c( "BusinessDevelopment","etc","HR", "IT","Others","Sales"))
survdiff(Surv(stag, event) ~ ProfessionGroup, data = data)

```

This group have significant difference p=0.03 -> Let's check another group


```{r}
#Profession group 1
data$ProfessionGroup_3j <- ifelse(data$profession == "IT" , "IT",
                               ifelse(data$profession == "HR", "HR",
                              ifelse(data$profession == "Commercial", "Commercial", "profession")
                            )
                        )
fit.KM.ProfessionGroup_3j<- survfit(Surv(stag, event) ~ ProfessionGroup_3j, data = data)
summary(fit.KM.ProfessionGroup_3j)
plot(fit.KM.ProfessionGroup_3j,col = 1:4, mark.time = TRUE,
     main = "Kaplan-Meier estimator for Profession groups 3",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomleft", col = 1:4, lty = 1, legend = c("Commecial", "HR", "IT","others"))
survdiff(Surv(stag, event) ~ ProfessionGroup_3j, data = data)
```
This group have p=0.008 so there at least one profession that give a difference 
But we can see that there is no enough data for Commercial + it's close to others jobs
But IT seems to be different from HR

```{r}
#Profession group 5j
data$ProfessionGroup_5J <- ifelse(data$profession == "HR" , "HR",
                        ifelse(data$profession == "IT", "IT",
                        ifelse(data$profession == "Commercial", "Commercial",
                        ifelse(data$profession == "Accounting", "Accounting",
                              ifelse(data$profession == "Engineer", "Engineer", "others")))))
                             
                      
fit.KM.ProfessionGroup_5J <- survfit(Surv(stag, event) ~ ProfessionGroup_5J , data = data)
summary(fit.KM.ProfessionGroup_5J )
plot(fit.KM.ProfessionGroup_5J ,col = 1:6, mark.time = TRUE,
     main = "Kaplan-Meier estimator for Profession groups",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomleft", col = 1:6, lty = 1, legend = c("Accounting", "Commercial","Engineer","HR","IT","Others"))
survdiff(Surv(stag, event) ~ ProfessionGroup_5J , data = data)

```
This group have p=0.001 so there at least one profession that give a difference
No enough data for Accounting and Engineer and Commercial
Let's focus on HR, IT and others



```{r}
#Profession HR vs IT vs Others
data$Profession_HR_IT_Oth <- ifelse(data$profession == "HR" , "HR",
                        ifelse(data$profession == "IT", "IT","Others"))
                      
new_fit.KM.Profession_HR_IT_Oth<- survfit(Surv(stag, event) ~ Profession_HR_IT_Oth, data = data)
summary(new_fit.KM.Profession_HR_IT_Oth)
                        
plot(new_fit.KM.Profession_HR_IT_Oth,col = 1:3, mark.time = TRUE,
     main = "Kaplan-Meier estimator for Profession groups HR VS IT VS OTHERS",
     ylab = "Staying employees probability",
     xlab = "time (Months)")
legend("bottomleft", col = 1:3, lty = 1, legend = c("HR","IT","Others"))
survdiff(Surv(stag, event) ~ Profession_HR_IT_Oth, data = data)
```


```{r}
#Group IT vs HR 

ProfessionOnlyHRandIT <- subset(data, Profession_HR_IT_Oth == "HR" | Profession_HR_IT_Oth == "IT" )

fit.KM.IT_HR<- survfit(Surv(stag, event) ~ Profession_HR_IT_Oth, data = ProfessionOnlyHRandIT)
summary(fit.KM.IT_HR)
                        
plot(fit.KM.IT_HR,col = 1:3, mark.time = TRUE,
     main = "Kaplan-Meier estimator for Profession groups IT VS HR ",
     ylab = "Staying employees probability",
     xlab = "time (Months)")
legend("bottomleft", col = 1:3, lty = 1, legend = c("HR","IT","Others"))
survdiff(Surv(stag, event) ~ Profession_HR_IT_Oth, data = ProfessionOnlyHRandIT)
```

#Extraversion --> good
```{r}

data$Extraversion_Group <- ifelse( data$extraversion < 6 , " NO Extraverted employee", "Extraverted Employee")

fit.KM.Extraversion_Group <-survfit(Surv(stag, event) ~ Extraversion_Group, data = data)
summary(fit.KM.Extraversion_Group)
plot(fit.KM.Extraversion_Group,col = 1:2, mark.time = TRUE,
     main = "Kaplan-Meier estimator for Extraverted employees group",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomleft", col = 1:2, lty = 1, legend = c("NO Extraverted employee", "Extraverted Employee"))
survdiff(Surv(stag, event) ~ Extraversion_Group, data = data)
```
The p value is 5e-04 <<5% so the Extraversion attitude have a impact on turnover employee

#Independence covariate
```{r}

data$Independence_Group <- ifelse( data$independ < 4 , " NO Independent employee", "Independent Employee")

fit.KM.Independence_Group <-survfit(Surv(stag, event) ~ Independence_Group, data = data)
summary(fit.KM.Independence_Group)
plot(fit.KM.Independence_Group,col = 1:2, mark.time = TRUE,
     main = "Kaplan-Meier estimator for Independent employees group",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomleft", col = 1:2, lty = 1, legend = c(" NO Independent employee", "Independent Employee"))
survdiff(Surv(stag, event) ~ Independence_Group, data = data)
```
 The p value is 0.002 <5% so the Independence attitude have a impact on turnover employee
 
 #Anxiety covariate
```{r}
data$Anxiety_Group <- ifelse( data$anxiety < 6 , " NO Anxious employee", "Anxious Employee")

fit.KM.Anxiety_Group <-survfit(Surv(stag, event) ~ Anxiety_Group, data = data)
summary(fit.KM.Anxiety_Group)
plot(fit.KM.Anxiety_Group,col = 1:2, mark.time = TRUE,
     main = "Kaplan-Meier estimator for Anxious employees group",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomleft", col = 1:2, lty = 1, legend = c(" NO Anxious employee", "Anxious Employee"))
survdiff(Surv(stag, event) ~ Anxiety_Group, data = data)
```
The p value is 0.006 <5% so the Anxiety attitude have a impact on turnover employee

 #Selfcontrol covariate 
```{r}
data$Selfcontrol_Group <- ifelse( data$selfcontrol < 6 , " NO Selfcontrol employee", "Selfcontrol Employee")

fit.KM.Selfcontrol_Group <-survfit(Surv(stag, event) ~ Selfcontrol_Group, data = data)
summary(fit.KM.Selfcontrol_Group)
plot(fit.KM.Selfcontrol_Group,col = 1:2, mark.time = TRUE,
     main = "Kaplan-Meier estimator for Selfcontrol employees group",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomleft", col = 1:2, lty = 1, legend = c("NO Selfcontrol employee", "Selfcontrol Employee"))
survdiff(Surv(stag, event) ~ Selfcontrol_Group, data = data)

```
The p value is 0.02 <5% so the Selfcontrol attitude have a impact on turnover employee

#Novation Covariates --> NOK
```{r}
data$Novation_Group <- ifelse( data$novator < 6 , "NO Novator employee", "Novator Employee")

fit.KM.Novation_Group <-survfit(Surv(stag, event) ~ Novation_Group, data = data)
summary(fit.KM.Novation_Group)
plot(fit.KM.Novation_Group,col = 1:2, mark.time = TRUE,
     main = "Kaplan-Meier estimator for Selfcontrol employees group",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomleft", col = 1:2, lty = 1, legend = c("NO Novator employee", "Novator Employee"))
survdiff(Surv(stag, event) ~ Novation_Group, data = data)

```
The p value is 0.3 >5% so the Novation attitude have NO impact on turnover employee

#Transport covariates
```{r}
fit.KM.Transport <- survfit(Surv(stag, event) ~ way, data = data)
                            
summary(fit.KM.Transport)
plot(fit.KM.Transport,col = 1:3, mark.time = TRUE,
     main = "Kaplan-Meier estimator for transport group",
     ylab = "Staying employees probability",
     xlab = "time (Months)")
legend("bottomright", col = 1:3, lty = 1, legend = c("Bus", "Car","Foot"))
survdiff(Surv(stag, event) ~ way, data = data)
```
the Transport group (Bus, car and foot) have a p value of 0.003 so it's significant

#Coach covariates --> NO
```{r}

fit.KM.Coach<- survfit(Surv(stag, event) ~ coach, data = data)
summary(fit.KM.Coach)
plot(fit.KM.Coach,col = 1:3, mark.time = TRUE,
     main = "Kaplan-Meier estimator for Coach",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomright", col = 1:3, lty = 1, legend = c("My head", "NO","Yes"))
survdiff(Surv(stag, event) ~ coach, data = data)
```
The Pvalue for Coach group is 0.2>5% so no big difference between 3 groups.
We can try to regroup The my head group with no coach 
We can conclude that having a coach or not, does not influence the employees turnover.

###Industry covariates
```{r}
fit.KM.Industry<- survfit(Surv(stag, event) ~ industry, data = data)
summary(fit.KM.Industry)
plot(fit.KM.Industry,col = 1:20, mark.time = TRUE,
     main = "Kaplan-Meier estimator for Industry ",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomright", col = 1:20, lty = 1, legend = c("Horeca", "Agri","Bank","Build","Consult","etc","IT","manufac","mining","Pharma","powermanag","realEstate","retail","state","telecom","transport"))
survdiff(Surv(stag, event) ~ industry, data = data)
```
 #We can conclude thet the industry have a big impact on the employee turnover Pvalue =2e-07 <<5%
 But need to regroup some industry to have more visible and  interpretable conclusion. 
 
 
 According to our previous distribution, we going to create an industry group containing the 6 highest industries with turnover-> Retail, Banks, Manufacture,etc, Consult and IT.
```{r}
#Powerfull industries:
data$Industry_HighT_Group <- ifelse(data$industry == "retail" , "retail",
                        ifelse(data$industry == "Banks", "Banks",
                        ifelse(data$industry == "manufacture", "manufacture",
                        ifelse(data$industry == "etc", "etc",
                        ifelse(data$industry == "Consult", "Consult",       
                              ifelse(data$industry == "IT", "IT", "others")
                              )
                        ))))
fit.KM.Industry_HighT_Group<- survfit(Surv(stag, event) ~ Industry_HighT_Group, data = data)
summary(fit.KM.Industry_HighT_Group)
plot(fit.KM.Industry_HighT_Group,col = 1:7, mark.time = TRUE,
     main = "Kaplan-Meier estimator for Industry groups with high Turnover",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomleft", col = 1:7, lty = 1, legend = c("Banks","Consult","etc","IT","manufacture", "Others"))
survdiff(Surv(stag, event) ~ Industry_HighT_Group, data = data)
```
The pvalue = 3e-06, this industry group have a significant impact on employee's turnover.
There is at least one industry having impact on this group! Let's find it.

Let's check the extrem industry in our previous plot, 1st = Banks + consult.

```{r}
#Banks + Consult:

Industry_Consult_Bank <- subset(data, data$Industry_HighT_Group == "Consult" | data$Industry_HighT_Group == "Banks" )
new_fit.KM.Industry_Consult_Bank<- survfit(Surv(stag, event) ~ Industry_HighT_Group, data = Industry_Consult_Bank)
summary(new_fit.KM.Industry_Consult_Bank)

plot(new_fit.KM.Industry_Consult_Bank,col = 1:2, mark.time = TRUE,
     main = "Kaplan-Meier estimator for Industry group Banks VS Consult",
     ylab = "Staying employee probability",
     xlab = "time (Months)")
legend("bottomleft", col = 1:2, lty = 1, legend = c("Banks","Consult"))
survdiff(Surv(stag, event) ~ Industry_HighT_Group, data = Industry_Consult_Bank)

```
The pvalue =0.6, so the Banks VS Consult group are not significant, we can group them together.


#Let's do same for etc, others and manufacture
```{r}
# etc VS others VS manufacture:

Industry_etc_manuf_oth <- subset(data, data$Industry_HighT_Group == "manufacture" | data$Industry_HighT_Group == "etc"| data$Industry_HighT_Group == "others" )

new_fit.KM.Industry_etc_manuf_oth<- survfit(Surv(stag, event) ~ Industry_HighT_Group, data = Industry_etc_manuf_oth)
summary(new_fit.KM.Industry_etc_manuf_oth)

plot(new_fit.KM.Industry_etc_manuf_oth,col = 1:2, mark.time = TRUE,
     main = "Kaplan-Meier estimator for Industry group etc VS manufacture VS others",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomleft", col = 1:2, lty = 1, legend = c("etc","manufacture","others"))
survdiff(Surv(stag, event) ~ Industry_HighT_Group, data = Industry_etc_manuf_oth)
```
Same us previously, this group can be grouped --> P=0.1


#Let's recode our  powerfull industries (group categories)

```{r}
                                                         
   Industry_Powerfull <- subset(data, data$Industry_HighT_Group == "Banks"| data$Industry_HighT_Group == "manufacture"| data$Industry_HighT_Group == "etc"| data$Industry_HighT_Group == "Consult"| data$Industry_HighT_Group == "IT"| data$Industry_HighT_Group == "others")                                                        


Industry_Powerfull$PowerIndustry <-ifelse(Industry_Powerfull$Industry_HighT_Group =="Banks","BCA",
                                ifelse(Industry_Powerfull$Industry_HighT_Group =="Consult","BCA",
                                        ifelse(Industry_Powerfull$Industry_HighT_Group =="etc","MOE",
                                               ifelse(Industry_Powerfull$Industry_HighT_Group =="manufacture","MOE",
                                                       ifelse(Industry_Powerfull$Industry_HighT_Group =="others","MOE",
                                                              ifelse(Industry_Powerfull$Industry_HighT_Group == "IT","IT","IT")
                                                                  )))))

new_fit.KM.Power_Industry<- survfit(Surv(stag, event) ~PowerIndustry, data =Industry_Powerfull)
summary(new_fit.KM.Power_Industry)

plot(new_fit.KM.Power_Industry,col = 1:3, mark.time = TRUE,
     main = "Kaplan-Meier estimator for powerfull grouped Industry BCA vs MOE vs IT ",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomleft", col = 1:3, lty = 1, legend = c("BCA","IT", "MOE"))
survdiff(Surv(stag, event) ~PowerIndustry, data =Industry_Powerfull)


```
The p= 5e-07  is highly significant = We have a significant industry groups in our model 
we can conclude that our group is successful. 
BCA = Banks+Consult
MOE= Manufacture + etc + Others
IT= IT

```{r}
###Data cleaning according to the previous study
Data_Clean <- data |>
  
    mutate ( 
       data$coach_gender <- NULL, #Pvalue is high for coach, coach_gender,greywage,traffic and novator attitude.
       data$coach<- NULL,
       data$gender<- NULL,
       data$novator<- NULL,
       data$greywage<- NULL,
       data$traffic<- NULL,
       Age  = factor(age > 35, levels = c(FALSE, TRUE),
                          labels = c("<=35", ">35")), 
       
       Profession = profession,
       Time = as.numeric(stag, units="Months"),
       Turnover = event,
       Status = event != "0",
       Transport = way,
       Industry=industry,
       Extraversion_Level = extraversion,
       Extraversion = factor(extraversion >= 6 , levels = c(FALSE, TRUE),
                             labels=c("Introverted", "Extraverted")),
       Independence_Level = independ,
       Independence = factor(independ >= 4, levels = c(FALSE, TRUE),
                             labels = c("No independent","Independent")),
       Selfcontrol_level = selfcontrol,
       Selfcontrol = factor( selfcontrol >= 6 ,levels = c(FALSE, TRUE),
                             labels=c(" NO Selfcontrol", "Selfcontrol")),
       Anxiety_Level = anxiety,
       Anxiety = factor(anxiety >= 6 , levels = c(FALSE, TRUE),
                        labels= c(" NO Anxious", "Anxious")) )|>
       
         
       
select(Time, Status,Age, Transport, Independence_Level, Independence,Extraversion_Level, Extraversion, Selfcontrol_level, Selfcontrol,Anxiety_Level, Anxiety, Turnover )


Data_Clean$Industry_HighT_Group <-ifelse(data$industry == "Banks", "Banks",
                        ifelse(data$industry == "manufacture", "manufacture",
                        ifelse(data$industry == "etc", "etc",
                        ifelse(data$industry == "Consult", "Consult",       
                              ifelse(data$industry == "IT", "IT", "others")
                              ))))


Data_Clean$PowerIndustry <- ifelse(Data_Clean$Industry_HighT_Group == "IT","IT",
                                ifelse(Data_Clean$Industry_HighT_Group =="Banks","BCA",
                                ifelse(Data_Clean$Industry_HighT_Group =="Consult","BCA",
                                        ifelse(Data_Clean$Industry_HighT_Group =="etc","MOE",
                                               ifelse(Data_Clean$Industry_HighT_Group =="manufacture","MOE","MOE" )))))
                                                       
                                                                 



Data_Clean$Profession_Group <- ifelse(data$profession == "HR" , "HR",
                        ifelse(data$profession == "IT", "IT","Others"))

#Data_Final <- subset(DataC, Profession_Group == "HR" | Profession_Group == "IT" )


```

```{r}
Data_Clean
```



#CoxPH Check------------------------------------------------------------- 

#Cox~Age:
```{r}
fit.cph.Age <- coxph(Surv(Time, Status)~Age , data= Data_Clean)
summary(fit.cph.Age)
```
 The cox model with age covariate is statistically significant for the 3 alternative tests with a pvalue <<<5%
 For Age more than 35Y the coef(beta) =0.505 = employee >35Y have more risk to stay in the same job than employees less than 35Y
 
 The hazard ration ex(beta) =1.65 = mean employees having more than 35Y increase the hazard by a factor of 1,65 to stay in their job
 + The P of Age covariate = 1.47e-07 = Age have a significant impact on the turnover
 
 
 
 
#Coxph Age + PowerIndustry:
```{r}

fit.cph.Age_PowerIndustry <- coxph(Surv(Time, Status) ~ Age + PowerIndustry, data = Data_Clean)
summary(fit.cph.Age_PowerIndustry)


```
The 3 alternatives tests gives a significants pvalue  p=5e-12 <<<5% = The model is significant 
The variable Age (>35) have a highly statistical significant coeff 3.06e-08 with a hazard ration of 1.71 Indicating a strong relationship between the Age (>35) and increasing the risk of staying in the same job.
In the other way, the pvalue of Industries --> IT or MOE are also  <<< than 5% with a HR of 0.4 and 0.6 with a big Confidence interval. = these results indicate that profession (IT and MOE) makes contribution to the difference in the Hazard Ratio after adjusting for the profession values and employees age

#Anxiety + Age
```{r}
fit.cph.Age_Anxiety <- coxph(Surv(Time, Status) ~ Age + Anxiety, data = Data_Clean)
summary(fit.cph.Age_Anxiety)
```
The Anxiety employee attitude have a significant impact on turnover.
Our model containing Age and Anxiety is significant -> with a likelihood ratio of p=6e-08 <<< 5%
+ The Pvalue of Age less than 35 years is equal to 1.35e-07 (Nothing changes, the age still have impact on the turnover) + 
The anxiety in this model play a role in turnover -> P = 0.006
#Selfcontrol + Age
```{r}
fit.cph_Selfcontrol<- coxph(Surv(Time, Status) ~ Age + Selfcontrol, data = Data_Clean)
summary(fit.cph_Selfcontrol)
```
#Exraversion + Age
```{r}
fit.cph.Age_Extraversion <- coxph(Surv(Time, Status) ~ Age + Extraversion, data = Data_Clean)
summary(fit.cph.Age_Extraversion)
```
#Independence + Age
```{r}
fit.cph.Age_Independence <- coxph(Surv(Time, Status) ~ Age + Independence, data = Data_Clean)
summary(fit.cph.Age_Independence)
```

The employees Attitudes give a good significant Pvalue, that's mean that employees attitude and age have a significant impact on employee's turnover.

#Transport 
```{r}
fit.cph.Age_Transport <-  coxph(Surv(Time, Status) ~ Age + Transport, data = Data_Clean)
summary(fit.cph.Age_Transport)
```



According to our study, we can see that we have a high risk of turnover with employee's having less than 35Y,Anxious, extraverted; working such an IT, etc...

We decide to create a column of a group of high risk and another one with low risk, with 2 variables (Age and Anxiety):

Note: different combination can be done! but let's focus in chosen one:

 #High risk Group and Low risk group 
```{r}
Data_Clean$RiskGroup_Age_Anxiety <-  ifelse( Data_Clean$Age ==  "<=35" & Data_Clean$Anxiety == "Anxious", "High Risk", "Low Risk")
```
 
```{r}

count(Data_Clean, RiskGroup_Age_Anxiety )
```


```{r}

fit.KM.RiskGroup_Age_Anxiety <- survfit(Surv(Time, Status) ~ RiskGroup_Age_Anxiety , data = Data_Clean)
summary(fit.KM.RiskGroup_Age_Anxiety )
plot(fit.KM.risk_group,col = 1:2, mark.time = TRUE,
     main = "Kaplan-Meier estimator for high and low risk groups",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomright", col = 1:2, lty = 1, legend = c("High risk", "Low risk"))
survdiff(Surv(Time, Status) ~ RiskGroup_Age_Anxiety , data = Data_Clean)
```
 the p= 7e-05 of our Risk group is significant! we can concluse that Age and Anxiety are a importants factors in turnover employee's.
 ####################################



Let's check Another group of risk:
High, medium and low risk, using Industries groups and Professions groups:
For high risk we take: Profession IT and Idustry IT, Medium = Industry MOE and Profession HR and finally Low risk = BCA for industry and Others for profession.
```{r}
Data_Clean$RiskGroup_Profession_Industry <-  ifelse( Data_Clean$PowerIndustry ==  "IT" & Data_Clean$Profession_Group == "IT", "High Risk", 
                                 ifelse( Data_Clean$PowerIndustry ==  "BCA" & Data_Clean$Profession_Group == "Others", "Low Risk","Medium Risk")) 
                                          
```

```{r}

count(Data_Clean, RiskGroup_Profession_Industry)
```

```{r}

fit.KM.RiskGroup_Profession_Industry <- survfit(Surv(Time, Status) ~ RiskGroup_Profession_Industry , data = Data_Clean)
summary(fit.KM.RiskGroup_Profession_Industry )
plot(fit.KM.risk_group,col = 1:3, mark.time = TRUE,
     main = "Kaplan-Meier estimator for high, Medium and low risk groups for Professions and industries",
     ylab = "Turnover probability",
     xlab = "time (Months)")
legend("bottomright", col = 1:3, lty = 1, legend = c("High risk", "Low risk","Medium Risk"))
survdiff(Surv(Time, Status) ~ RiskGroup_Profession_Industry , data = Data_Clean)
```
```{r}
#Export Data_Clean.csv
write.table(Data_Clean, file = "Data_Clean.csv", sep=",")
```






#Logistic Regression Model:
In a linear regression model, the probability of the response variable is modeled as a linear combination of predictors and multiplicative coefficients. The encoding of the response variable (Survived) as 0 and 1 allows for a linear regression model but covariates that produce a response greater than 1 and less than 0 are considered errors and can negatively impact parameter estimation. In logistic regression, the probability of the response variable is modeled with the logistic function, or y = eX/(1+eX). Logistic regression is a classic model for binary classification.

A Logistic model was done in python:




